Management induced changes of soil organic carbon on global croplands

### 2020-12-11 SOCbudgetPaper/appendix.Rmd
shortened verion of appendix

## table on method subsections to functions within R packages {#append:subsection2mrfunctions}

## table on mapping LUH2FAO2MAG {#append:Tableluh2fao2mag}

## kcr2kres mapping {#append:Tablekcr2kres}

## carbon 2 dry matter {#append:Tablec2dm}
Litter is coming from LPJmL in carbon units - transformation with 0.44 is done twice reverting the effect of the transformation

@@

>>>>

## carbon 2 dry matter {#append:Tablec2dm}

@@

## regional SOC stock in GtC from different sources {#append:regcompare}

```{r captionregSOCtable, echo=FALSE}
captionregSOCtable <- "Modelled as well as data based estimation for global SOC stock in GtC for the first 30 cm of soil aggregated over all land area. Note that SoilGrids, GSOC and WISE do not consider changes over time and rely on soil profile data gather over a long period of time, which makes it hard to pinpoint a specific year to these SOC estimations. In this context they will be compared to modelled data (LPJmL4, this study) for the year 2010."
```

```{r regSOCtable, out.width = "100%", fig.cap = captionregSOCtable, echo=FALSE, fig.pos="H"}
# All defaults
knitr::include_graphics("../ResultNotebooks/Output/Images/reg_comparisonfigure.png")
```

with 
Canada, Australia and New Zealand: CAZ; 
China: CHA; 
European Union: EUR; 
India: IND; 
Japan: JPN; 
Latin America: LAM;
Middle East and north Africa: MEA; 
non-EU member states: NEU;
other Asia: OAS; reforming countries: REF; Sub-Saharan Africa:
SSA; United States: USA.

## global SOC debt in GtC for various litter parameterizations {#append:senslitterpnv}
